Combinatorics of the geometry of Wilson loop diagrams

### 2018-12-21 General WLD combinatorics.tex
is this ok now (with comment)
a few small things at the beginning of section 4

For any $e \not\in F$, we certainly have $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C) +1$ since $F$ is a flat. Now let $e \in C$, and suppose that $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C)$. This implies that $(F\setminus C)\cup \{e\}$ is dependent, and hence contains a circuit, $S$. This circuit must contain at least one element but this contradicts the fact that $C$ was the union of all circuits in $F$.

@@

\begin{algorithm}\label{alg WLD to denom via GN}
Let $W = (\cP,n)$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn} (see Section~\ref{section background}).
\begin{itemize}
  \item For each $i \in \interval{1}{n}$, we construct a factor $r_i$ as follows:
    \begin{itemize}
      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.  (By convention set $I_{-1}=I_n$.)  Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.  Write $I_{i}(p)$ for the vertex associated to propagator $p$ under this bijection.
      \item Let $S_i = \{p \in \cP \ | \ I_{i-1}(p) \neq I_i(p)\}$. (By convention, set $I_{-1} = I_n$.)
	  \item Write $\Delta_{I_i}$ for the determinant of the $k \times k$ minor of $C(W)$ with columns indexed by $I_i$.
      \item Let $r_i$ be $\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
    \end{itemize}
  \item Define $R = \prod_{i=1}^n r_i$.
\end{itemize}
\end{algorithm}
\note{What are we doing about the sign of the determinants?}

\begin{figure}
\includegraphics{egWLD_forR}
\caption{Example WLD for illustrating Algorithm~\ref{alg WLD to denom via GN} and bijections between propagators and vertices for each Grassmann necklace element.}\label{fig R eg}
\end{figure}
\todo{I've named the propagators $p$, $q$, $s$; could whoever codes up the figure please add that?}

\begin{eg}
Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $s$ to rows $1,2,3$ respectively, we obtain the matrix
\[
C(W) = \begin{bmatrix} a & b & 0 & 0 & 0 & c & d \\ e & f & 0 & 0 & g & h & 0 \\ i & j & 0 & k & l & 0 & 0 \end{bmatrix}
\]
The Grassmann necklace of this diagram is 
\begin{gather*}I_1 = \{1,2,4\}, I_2 = \{2,4,5\}, I_3 = \{4,5,6\}, I_4=\{4,5,6\},\\ I_5=\{5,6,7\}, I_6 = \{6,7,1\}, I_7=\{7,1,2\}. \end{gather*}  
Figure~\ref{fig R eg} also indicates the pairings between propagators and vertices for each $i \in \interval{1}{7}$.

>>>>

\note{the one element could be e so this doesn't work}
For any $e \not\in F$, we certainly have $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C) +1$ since $F$ is a flat. Now let $e \in C$, and suppose that $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C)$. This implies that $(F\setminus C)\cup \{e\}$ is dependent, and hence contains a circuit, $S$. This circuit must contain at least one element but this contradicts the fact that $C$ was the union of all circuits in $F$.

@@

\begin{algorithm}\label{alg WLD to denom via GN}
Let $W = (\cP,n)$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn} (see Section~\ref{section background}).
\begin{itemize}
  \item For each $i \in [n]$, we construct a factor $r_i$ as follows:
    \begin{itemize}
      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.  (By convention set $I_{-1}=I_n$.)  Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.  Write $I_{i}(p)$ for the vertex associated to propagator $p$ under this bijection.
      \item Let $S_i = \{p \in \cP \ | \ I_{i-1}(p) \neq I_i(p)\}$. (By convention, set $I_{-1} = I_n$.)
	  \item Write $\Delta_{I_i}$ for the determinant of the $k \times k$ minor of $C(W)$ with columns indexed by $I_i$.
      \item Let $r_i$ be $\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
    \end{itemize}
  \item Define $R = \prod_{i=1}^n r_i$.
\end{itemize}
\end{algorithm}
\note{What are we doing about the sign of the determinants?  --- in the end we are making a denominator, so an object that probably makes the most sense as being defined up to sign; I would suggest having all this be up to an overall sign, but perhaps we can discuss in our next meeting.}

\begin{figure}
\includegraphics{egWLD_forR}
\caption{Example WLD for illustrating Algorithm~\ref{alg WLD to denom via GN} and bijections between propagators and vertices for each Grassmann necklace element.}\label{fig R eg}
\end{figure}

\begin{eg}
Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $s$ to rows $1,2,3$ respectively, we obtain the matrix
\[
C(W) = \begin{bmatrix} a & b & 0 & 0 & 0 & c & d \\ e & f & 0 & 0 & g & h & 0 \\ i & j & 0 & k & l & 0 & 0 \end{bmatrix}
\]
The Grassmann necklace of this diagram is 
\begin{gather*}I_1 = \{1,2,4\}, I_2 = \{2,4,5\}, I_3 = \{4,5,6\}, I_4=\{4,5,6\},\\ I_5=\{5,6,7\}, I_6 = \{6,7,1\}, I_7=\{7,1,2\}. \end{gather*}  
Figure~\ref{fig R eg} indicates the pairings between propagators and vertices for each $i \in [1,7]$.
